How to Learn Useful Changes to Software Projects\\(to Reduce Runtimes and Software Defects)

### 2015-08-28 tex/algos.tex
Updates from ShareLaTeX

	For  continuous and discrete values,
the {\em variability} can be measured using standard deviation $\sigma$ or entropy $e$.
Note that \mbox{$\sigma = \sqrt{\sum^n_{i=1} \left( \frac{x_i - \bar{x})^2}{n-1}\right)}$}
where $\bar{x}$ is the mean of  numeric features $x_1,x_2,..x_n$.
Also \mbox{$e = - \sum^n_{i=1} p_i \mathit{log}_2(p_i)$} 
for  $n$ discrete values  at frequency
$f_1,f_2,.. f_n$ for \mbox{$N = \sum^n_{i=1} f_i$} and $p_i = f_i/N$.

@@

				WHERE  divides data into  groups of size $\alpha=\sqrt{N}$ using 
		Using this measure, WHERE runs as follows:
		\begin{enumerate}[leftmargin=3mm]
			\item Find   two   distance cases,  $X,Y$
			by picking any case $W$ at random, then setting $X$ to its most
			distant case, then setting $Y$ to the case most distant from
			$X$
			(which requires only $O(2N)$ comparisons).
			\item Project each case $Z$
			to position $x$ on a    lines running from $X$ to $Y$: if $a,b$  are distances  $Z$ to $X,Y$  then  $x = (a^2+c^2 - b^2)/(2ac)$.
			\item Split the data at the median $x$ value of all cases.
			\item For   splits larger than  $\alpha=\sqrt{N}$, recurse   from step1.
		\end{enumerate}
 In terms of related work,
	  the above is similar in approach to Boley's PDDP algorithm~\cite{boley98}, but PDDP requires an $O(N^2)$ calculation
	  at each recursive level to find the PCA principle component. Our method, on the other hand,
	  performs the same task with only $O(2N)$ distance calculations 	using the 
	  FASTMAP heuristic~\cite{Faloutsos1995} shown in step1. Platt~\cite{platt05} notes that FASTMAP is a  Nystr\"om approximation to the first component of PCA.

@@

	Find a split in the values of  independent features that most reduces the variability
  of the dependent feature (measured using \fig{where}.A). Divide data on that  feature's split and 
   for all splits bigger than $\alpha=\sqrt{N}$,  recurses on each split.

>>>>

	For  continuous and discrete values,
the {\em variability} can be measured using standard deviation $\sigma$ or entropy $e$.
Note that \mbox{$\sigma = \sqrt{\sum^n_{i=1} \left( \frac{(x_i - \bar{x})^2}{n-1}\right)}$}
where $\bar{x}$ is the mean of  numeric features $x_1,x_2,..x_n$.
Also \mbox{$e = - \sum^n_{i=1} p_i \mathit{log}_2(p_i)$} 
for  $n$ discrete values  at frequency
$f_1,f_2,.. f_n$ for \mbox{$N = \sum^n_{i=1} f_i$} and $p_i = f_i/N$.

@@

				WHERE  divides data into  groups of size $\alpha=\sqrt{N}$. 
		Using this measure, WHERE runs as follows:
		\begin{enumerate}[leftmargin=3mm]
			\item Find   two   distance cases,  $X,Y$
			by picking any case $W$ at random, then setting $X$ to its most
			distant case, then setting $Y$ to the case most distant from
			$X$
			(which requires only $O(2N)$ comparisons).
			\item Project each case $Z$
			to position $x$ on a    lines running from $X$ to $Y$: if $a,b$  are distances  $Z$ to $X,Y$  then  $x = (a^2+c^2 - b^2)/(2ac)$.
			\item Split the data at the median $x$ value of all cases.
			\item For   splits larger than  $\alpha=\sqrt{N}$, recurse   from step1.
		\end{enumerate}
 In terms of related work,
	  the above is similar in approach to Boley's PDDP algorithm~\cite{boley98}, but PDDP requires an $O(N^2)$ calculation
	  at each recursive level to find the PCA principle component. Our method, on the other hand,
	  performs the same task with only $O(2N)$ distance calculations 	using the 
	  FASTMAP heuristic~\cite{Faloutsos1995} shown in step1. Platt~\cite{platt05} notes that FASTMAP is a  Nystr\"om approximation to the first component of PCA.

@@

	Find a split in the values of  independent features that most reduces the variability
  of the dependent feature (measured using \fig{where}.A). Contruct a tree using these splits.

### 2015-08-28 tex/prediction_stats.tex
Updates from ShareLaTeX

	\caption{Training and test {\em data set properties} for  Jureczko data ,
		sorted by \% defective examples.
		On the right-hand-side, we show the {\em results from learning}.
		Data is ``good'' if it has recall over 60\% and false alarm under 40\%
		(and note that, after tuning, there are more ``good'' than before).
	Results  	\colorbox{celadon}{ marked with ``$\star$''} show large improvements in performance, after tuning
		(lower {\em pf} or higher {\em pd}).
		The data in  the  \colorbox{lavenderpink}{three bottom rows}, marked with ``$\times$'', are ``not good'' since their test suites  have so few non-defective examples (less than 5\% of the total sample) that it becomes harder to find better data towards which we can displace test data.
	}\label{fig:j}
\end{figure*}

>>>>

	\caption{Training and test {\em data set properties} for  Jureczko data ,
		sorted by \% defective examples.
		On the right-hand-side, we show the {\em results from learning}.
		Data is usable if it has a recall of 60\% or more and false alarm of 30\% or less (and note that, after tuning, there are more usable data sets than before). Results  	\colorbox{celadon}{ marked with ``$\star$''} show large improvements in performance, after tuning
		(lower {\em pf} or higher {\em pd}).
		Data in  the  \colorbox{lavenderpink}{three bottom rows}, marked with ``$\times$'', are  performing
		poorly-- that data so few non-defective examples  that it  is hard for
		our learners to distinguish between classes.
	}\label{fig:j}
\end{figure*}

### 2015-08-28 tex/results_models.tex
Updates from ShareLaTeX

\begin{figure}[!t]
%\noindent\begin{minipage}{0.5\textwidth} 
{\small 
\begin{tabular}{llrrc}
\arrayrulecolor{lightgray}
\textbf{Rank} & \textbf{Treatment} & \textbf{50th} & \textbf{25-75th} & \\\hline
  1 &          BIC &    -3.3  &  2.2 & \quart{26}{2}{27}{32} \\
  1 &      CD &    -2.9  &  11.7 & \quart{17}{14}{28}{32} \\
  1 &      CD+FS &    -2.75  &  65.5 & \quart{0}{78}{28}{32} \\
\hline  2 &        XTREE &    51.5  &  14.84 & \quart{82}{17}{93}{32} \\
\end{tabular}}
\caption{Methods 1,2,3,4 applied to some ground-truth data (in this case, the POM3 model).
Values collected from  40 repeated runs of each method with different random seeds.
Results show the efficacy of XTREE in reducing the total overall cost in the original test data, when other planners fail to do so.
}\label{fig:coc}
\end{figure}

>>>>

\begin{figure}[!t]
%\noindent\begin{minipage}{0.5\textwidth} 
{\small 
\begin{tabular}{llrrc}
\arrayrulecolor{lightgray}
\rowcolor{lightgray}\textbf{Rank} & \textbf{Treatment} & \textbf{Median} & \textbf{IQR} & \\\hline
  1 &        XTREE &   59   &  9 & \quart{75}{4}{78}{99} \\
\hline   2 &      BIC &    5  & 1  & \quart{44}{0}{44}{99} \\
2 &          CD+FS & -7  & 100  & \quart{0}{53}{43}{99} \\   
2 &      CD &    -9  &  77 & \quart{21}{41}{42}{99} \\
\hline \end{tabular}}
\caption{Methods 1,2,3,4 applied to some ground-truth data (in this case, the POM3 model).
Values collected from  40 repeated runs of each method with different random seeds.
Results show the efficacy of XTREE in reducing the total overall cost in the original test data, when other planners fail to do so.}\label{fig:coc}
\end{figure}
